DOM bridges and barriers: systematic review and survey

### 2025-10-15 reports/draft_results.qmd
update from props

![](images/bridges_old.png){fig-align="center" width="70%"}

![](images/barriers_old.png){fig-align="center" width="70%"}

@@

Code appearance frequencies across all bridge **OR** barrier codes. The proportions reported in these figures represent the percent of codes that theme or sub-theme comprises.

@@

code_sum <- code_freq %>%
  group_by(bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(code_cat) %>% 
  mutate(n_subtotal = sum(total)) %>%
  summarise(value = n_subtotal/n_total) %>%
  rename("br_ba" = code_cat) %>%
  mutate(percent_label = scales::percent(value, accuracy = 1), 
         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier", value, -value),
         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA))), 
         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge"), "bridge", "barrier")) %>%
  group_by(code_level) %>%
  distinct()

code_sum$code_level <- factor(code_sum$code_level, levels = c("Social bridge or barrier", "Ecological bridge or barrier", "Data bridge or barrier"))
code_sum$code_brba <- factor(code_sum$code_brba, levels = c("bridge", "barrier"))

ggplot(code_sum, aes(x = code_level, 
             y = percent,
             fill = code_brba)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = percent_label),
            position = position_stack(vjust = 0.65),
            color = "black", 
            size = 5) +
  ylim(-0.4,0.7)+
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x =element_blank(),
        axis.text.y = element_text(size = 20, color = "black"),
        panel.grid = element_blank(),
        legend.position = c(-0.17, 0.99),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.y.right = element_text(angle = 0, size = 16)) +
  geom_hline(yintercept = 0.0, linewidth = 1) + 
  labs(fill = "")+ 
  guides(fill = guide_legend(nrow = 1))

#ggsave("figures/ms_figs/all_freq/all_freq.png", width = 8, height = 5, units = ("in"))
```

@@

#reformat data
code_sum_br <- code_freq %>%
  filter(bridge_barr == "Bridge") %>%
  mutate(n_total = sum(total)) %>%
  group_by(code_cat, code_name) %>%
  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
  mutate(percent = scales::percent(value, accuracy = 1), 
         code_name = factor(code_name)) %>%
  ungroup() %>%
  group_by(code_cat) %>%
  arrange(code_name, desc(percent))

#plot
br_freq <- ggplot(code_sum_br, aes(x = value*100, y = reorder(code_name, value))) + 
  geom_point(size = 5, color = "goldenrod") + 
  # scale_x_continuous(limits = c(0, 30), 
  #                    breaks = seq(0, 30, 5), 
  #                    name = "Percent appearance (%)") +
  theme_minimal() +
  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
  scale_x_reverse(limits = c(30, 0), 
                  #breaks = seq(0, 30, 5), 
                  name = "Percent appearance (%)")+
  theme(strip.placement = "outside",
        strip.text = element_text(face = "bold", size = 14, hjust = 0), 
        axis.text = element_text(size = 12, color = "black"), 
        axis.title = element_text(size = 14, color = "black")) +
  ylab("")

@@

#reformat data
code_sum_ba <- code_freq %>%
  filter(bridge_barr == "Barrier") %>%
  mutate(n_total = sum(total)) %>%
  group_by(code_cat, code_name) %>%
  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
  mutate(percent = scales::percent(value, accuracy = 1), 
         code_name = factor(code_name)) %>%
  ungroup() %>%
  group_by(code_cat) %>%
  arrange(code_name, desc(percent))

#plot
ba_freq <- ggplot(code_sum_ba, aes(x = value*100, y = reorder(code_name, value))) + 
  geom_point(size = 5, color = "lightskyblue3") + 
  scale_x_continuous(limits = c(0, 30), 
                     breaks = seq(0, 30, 10), 
                     name = "Percent appearance (%)") +
  scale_y_discrete(position = "right") +
  theme_minimal() +
  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
  theme(strip.placement = "outside",
        strip.text = element_text(face = "bold", size = 14, hjust = 1), 
        axis.text = element_text(size = 12, color = "black"), 
        axis.title = element_text(size = 14, color = "black")) +
  ylab("")

#ggsave("figures/ms_figs/all_freq/ba_freq.png", width = 8, height = 8, units = c("in"))

@@

#theme bridge/barrier
code_sum_s <- code_freq_s %>%
  group_by(bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(code_cat) %>% 
  mutate(n_subtotal = sum(total)) %>%
  summarise(value = n_subtotal/n_total) %>%
  rename("br_ba" = code_cat) %>%
  mutate(percent_label = scales::percent(value, accuracy = 1), 
         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier" | br_ba == "Implementation barrier", value, -value),
         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", 
                              if_else(br_ba %in% c("Implementation bridge", "Implementation barrier"), "Implementation bridge or barrier", NA)))), 
         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge"), "bridge", "barrier")) %>%
  group_by(code_level) %>%
  distinct()

code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Implementation bridge or barrier", "Social bridge or barrier", "Ecological bridge or barrier", "Data bridge or barrier"))
code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("bridge", "barrier"))

all_freq_survey <- ggplot(code_sum_s, aes(x = code_level, 
             y = percent,
             fill = code_brba)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = percent_label),
            position = position_stack(vjust = 0.65),
            color = "black", 
            size = 5) +
  ylim(-0.55,0.7)+
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x =element_blank(),
        axis.text.y = element_text(size = 26, color = "black"),
        panel.grid = element_blank(),
        legend.position = c(-0.17, 0.99),
        legend.text = element_text(size = 20, color = "black"),
        strip.text.y.right = element_text(angle = 0, size = 18)) +
  geom_hline(yintercept = 0.0, linewidth = 1) + 
  labs(fill = "")+ 
  guides(fill = guide_legend(nrow = 1))

#ggsave("figures/ms_figs/all_freq/all_freq_survey.png", width = 13, height = 8, units = ("in"))

@@

code_sum_br_s <- code_freq_s %>%
  filter(bridge_barr == "Bridge") %>%
  mutate(n_total = sum(total)) %>%
  group_by(code_cat, code_name) %>%
  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
  mutate(percent = scales::percent(value, accuracy = 1), 
         code_name = factor(code_name)) %>%
  ungroup() %>%
  group_by(code_cat) %>%
  arrange(code_name, desc(percent))

#plot
br_freq_s <- ggplot(code_sum_br_s, aes(x = value*100, y = reorder(code_name, value))) + 
  geom_point(size = 5, color = "goldenrod") + 
  # scale_x_continuous(limits = c(0, 30), 
  #                    breaks = seq(0, 30, 5), 
  #                    name = "Percent appearance (%)") +
  theme_minimal() +
  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
  scale_x_reverse(limits = c(20, 0), 
                  #breaks = seq(0, 30, 5), 
                  name = "Percent appearance (%)")+
  theme(strip.placement = "outside",
        strip.text = element_text(face = "bold", size = 14, hjust = 0), 
        axis.text = element_text(size = 12, color = "black"), 
        axis.title = element_text(size = 14, color = "black")) +
  ylab("")

@@

#barrier freq
#reformat data
code_sum_ba_s <- code_freq_s %>%
  filter(bridge_barr == "Barrier") %>%
  mutate(n_total = sum(total)) %>%
  group_by(code_cat, code_name) %>%
  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
  mutate(percent = scales::percent(value, accuracy = 1), 
         code_name = factor(code_name)) %>%
  ungroup() %>%
  group_by(code_cat) %>%
  arrange(code_name, desc(percent))

#plot
ba_freq_s <- ggplot(code_sum_ba_s, aes(x = value*100, y = reorder(code_name, value))) + 
  geom_point(size = 5, color = "lightskyblue3") + 
  scale_x_continuous(limits = c(0, 20), 
                     breaks = seq(0, 20, 10), 
                     name = "Percent appearance (%)") +
  scale_y_discrete(position = "right") +
  theme_minimal() +
  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
  theme(strip.placement = "outside",
        strip.text = element_text(face = "bold", size = 16, hjust = 1), 
        axis.text = element_text(size = 12, color = "black"), 
        axis.title = element_text(size = 14, color = "black")) +
  ylab("")

#ggsave("figures/ms_figs/all_freq/ba_freq_survey.png", width = 6, height = 9, units = c("in"))

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 5
#| fig-align: center

@@

ggplot(code_rel_melt_h, aes(x = code1, y = reorder(code2, total))) +
geom_tile(aes(fill = total, colour = bor_box)) + 
scale_fill_gradient2(high = "red")+
ylab("")+
xlab("")+
labs(fill = "Number of co-occurences")+
theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 14, face = "bold", color = x_colors[levels(code_rel_melt_h$code1)]), 
      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]), 
      panel.background = element_blank())+
geom_text(aes(label = total))+
scale_color_manual(values = c("black", "#00000000"))+
guides(color = "none")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 5
#| fig-align: center

@@

consv <- codes_LU %>%
  gather(col, consv_topic, reason1:reason3) %>%
  subset(select = consv_topic)

@@

consv_bar
```

@@

#ggsave("figures/ms_figs/industry/stack_survey.png", width = 7, height = 6, units = c("in"))

#radar plots
freq_job_survey3 <- freq_job_survey %>%
  group_by(fish_ship, bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(fish_ship, bridge_barr, code_name) %>% 
  mutate(n_subtotal = sum(total)) %>%
  reframe(value = (n_subtotal/n_total)*100) %>%
  ungroup() %>%
  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-c(id))

@@

top_bridge <- freq_job_survey3 %>%
  subset(code_name %in% top_survey$code_name) %>% 
  filter(bridge_barr == "Bridge") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

top_barrier <- freq_job_survey3 %>%
  subset(code_name %in% top_survey$code_name) %>%
  filter(bridge_barr == "Barrier") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

ggradar::ggradar(top_bridge,
        values.radar = c(0, 16, 22), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_br_survey.png", height = 8, width = 8, units = c("in"))

ggradar::ggradar(top_barrier,
        values.radar = c(0, 17, 28), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))

@@

#radar plots
freq_job_lit3 <- freq_job_lit %>%
  group_by(fish_ship, bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(fish_ship, bridge_barr, code_name) %>% 
  mutate(n_subtotal = sum(total)) %>%
  reframe(value = (n_subtotal/n_total)*100) %>%
  ungroup() %>%
  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-c(id))

@@

top_bridge <- freq_job_lit3 %>%
  subset(code_name %in% top_lit$code_name) %>% 
  filter(bridge_barr == "Bridge") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

top_barrier <- freq_job_lit3 %>%
  subset(code_name %in% top_lit$code_name) %>%
  filter(bridge_barr == "Barrier") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

ggradar::ggradar(top_bridge,
        values.radar = c(0, 8, 16), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 17, 37), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

>>>>

![](images/sunburst.png){fig-align="center" width="100%"}

@@

Code appearance counts across all bridge **OR** barrier codes. The values represent counts of themes or sub-themes.

@@

  code_sum <- code_freq %>%
  #mutate(n_total = sum(total)) %>%
  #group_by(code_cat) %>% 
  #mutate(n_subtotal = sum(total)) %>%
  #summarise(value = n_subtotal/n_total) %>%
  rename("br_ba" = code_cat) %>%
  # mutate(percent_label = scales::percent(value, accuracy = 1), 
  #        percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier", value, -value),
  #        code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
  #                             if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
  #                             if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA))), 
  #        code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge"), "bridge", "barrier")) %>%
  mutate(percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier", -total, total),
         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological", 
                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data",
                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social", NA))), 
         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge"), "bridge", "barrier")) %>%
  group_by(code_brba, code_level) %>%
  summarize(value = sum(percent)) %>%
  mutate(value_label = ifelse(code_brba == "barrier", value*-1, value)) %>%
  distinct()

code_sum$code_level <- factor(code_sum$code_level, levels = c("Social", "Ecological", "Data"))
code_sum$code_brba <- factor(code_sum$code_brba, levels = c("barrier", "bridge"))

ggplot(code_sum, aes(x = code_level, 
             y = value,
             fill = code_brba)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = value_label),
            position = position_stack(vjust = 0.5),
            color = "black", 
            size = 5) +
  #ylim(-0.4,0.7)+
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Barrier", "Bridge")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x =element_blank(),
        axis.text.y = element_text(size = 20, color = "black"),
        panel.grid = element_blank(),
        legend.position = c(-0.05, 1),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.y.right = element_text(angle = 0, size = 16)) +
  geom_hline(yintercept = 0.0, linewidth = 1) + 
  labs(fill = "")+ 
  guides(fill = guide_legend(nrow = 1))

#ggsave("figures/ms_figs/all_freq/all_freq.png", width = 8, height = 6, units = ("in"))
#ggsave("figures/slides_svg/freq_lit.svg", width = 8, height = 6, units = ("in"))
```

@@

#reformat data
code_sum_br <- code_freq %>%
  filter(bridge_barr == "Bridge") %>%
  #mutate(n_total = sum(total)) %>%
  #group_by(code_cat, code_name) %>%
  #summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
  mutate(#percent = scales::percent(value, accuracy = 1), 
         code_name = factor(code_name)) %>%
  ungroup() %>%
  group_by(code_cat) %>%
  arrange(code_name, desc(total))

#plot
br_freq <- ggplot(code_sum_br, aes(x = total, y = reorder(code_name, total))) + 
  geom_point(size = 5, color = "lightskyblue3") + 
  # scale_x_continuous(limits = c(0, 30), 
  #                    breaks = seq(0, 30, 5), 
  #                    name = "Percent appearance (%)") +
  theme_minimal() +
  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
  scale_x_continuous(limits = c(0, 75), 
                  #breaks = seq(0, 30, 5), 
                  name = "Sub-theme count (#)")+
  scale_y_discrete(position = "right") +
  theme(strip.placement = "outside",
        strip.text = element_text(face = "bold", size = 14, hjust = 0), 
        axis.text = element_text(size = 12, color = "black"), 
        axis.title = element_text(size = 14, color = "black")) +
  ylab("")

@@

#reformat data
code_sum_ba <- code_freq %>%
  filter(bridge_barr == "Barrier") %>%
  #mutate(n_total = sum(total)) %>%
  #group_by(code_cat, code_name) %>%
  #summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
  mutate(#percent = scales::percent(value, accuracy = 1), 
         code_name = factor(code_name)) %>%
  ungroup() %>%
  group_by(code_cat) %>%
  arrange(code_name, desc(total))

#plot
ba_freq <- ggplot(code_sum_ba, aes(x = total, y = reorder(code_name, total))) + 
  geom_point(size = 5, color = "goldenrod") + 
  scale_x_reverse(limits = c(75, 0), 
                     breaks = seq(0,60, 20), 
                     name = "Sub-theme count (#)") +
  theme_minimal() +
  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
  theme(strip.placement = "outside",
        strip.text = element_text(face = "bold", size = 14, hjust = 1), 
        axis.text = element_text(size = 12, color = "black"), 
        axis.title = element_text(size = 14, color = "black")) +
  ylab("")

#ggsave("figures/ms_figs/all_freq/ba_freq.png", width = 7.5, height = 8, units = c("in"))

@@

#theme bridge/barrier
 code_sum_s <- code_freq_s %>%
  rename("br_ba" = code_cat) %>%
  mutate(percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier" | br_ba == "Implementation barrier", -total, total),
         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological", 
                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data",
                              if_else(br_ba %in% c("Implementation barrier", "Implementation bridge"), "Implementation",
                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social", NA)))),
         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge"), "bridge", "barrier")) %>%
  group_by(code_brba, code_level) %>%
  summarize(value = sum(percent)) %>%
  mutate(value_label = ifelse(code_brba == "barrier", value*-1, value)) %>%
  distinct()

code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Implementation", "Social", "Ecological", "Data"))
code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("barrier", "bridge"))

all_freq_survey <- ggplot(code_sum_s, aes(x = code_level, 
             y = value,
             fill = code_brba)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = value_label),
            position = position_stack(vjust = 0.5),
            color = "black", 
            size = 5) +
  #ylim(-0.55,0.7)+
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Barrier", "Bridge")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x =element_blank(),
        axis.text.y = element_text(size = 20, color = "black"),
        panel.grid = element_blank(),
        legend.position = c(-0.05, 1),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.y.right = element_text(angle = 0, size = 16)) +
  geom_hline(yintercept = 0.0, linewidth = 1) + 
  labs(fill = "")+ 
  guides(fill = guide_legend(nrow = 1))

#ggsave("figures/ms_figs/all_freq/all_freq_survey.png", width = 8, height = 6, units = ("in"))
#ggsave("figures/slides_svg/freq_survey.svg", width = 8, height = 6, units = ("in"))

@@

code_sum_br_s <- code_freq_s %>%
  filter(bridge_barr == "Bridge") %>%
  #mutate(n_total = sum(total)) %>%
  #group_by(code_cat, code_name) %>%
  #summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
  mutate(#percent = scales::percent(value, accuracy = 1), 
         code_name = factor(code_name)) %>%
  ungroup() %>%
  group_by(code_cat) %>%
  arrange(code_name, desc(total))

#plot
br_freq_s <- ggplot(code_sum_br_s, aes(x = total, y = reorder(code_name, total))) + 
  geom_point(size = 5, color = "lightskyblue3") + 
  # scale_x_continuous(limits = c(0, 30), 
  #                    breaks = seq(0, 30, 5), 
  #                    name = "Percent appearance (%)") +
  theme_minimal() +
  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
  scale_x_continuous(limits = c(0, 20), 
                  #breaks = seq(0, 30, 5), 
                  name = "Sub-theme count (#)")+
  scale_y_discrete(position = "right") +
  theme(strip.placement = "outside",
        strip.text = element_text(face = "bold", size = 14, hjust = 0), 
        axis.text = element_text(size = 12, color = "black"), 
        axis.title = element_text(size = 14, color = "black")) +
  ylab("")

@@

#barrier freq
#reformat data
code_sum_ba_s <- code_freq_s %>%
  filter(bridge_barr == "Barrier") %>%
  #mutate(n_total = sum(total)) %>%
  #group_by(code_cat, code_name) %>%
  #summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
  mutate(#percent = scales::percent(value, accuracy = 1), 
         code_name = factor(code_name)) %>%
  ungroup() %>%
  group_by(code_cat) %>%
  arrange(code_name, desc(total))

#plot
ba_freq_s <- ggplot(code_sum_ba_s, aes(x = total, y = reorder(code_name, total))) + 
  geom_point(size = 5, color = "goldenrod") + 
  scale_x_reverse(limits = c(20, 0), 
                     breaks = seq(0, 20, 5), 
                     name = "Sub-theme count (#)") +
  theme_minimal() +
  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
  theme(strip.placement = "outside",
        strip.text = element_text(face = "bold", size = 14, hjust = 1), 
        axis.text = element_text(size = 12, color = "black"), 
        axis.title = element_text(size = 14, color = "black")) +
  ylab("")

#ggsave("figures/ms_figs/all_freq/ba_freq_survey.png", width = 6, height = 8, units = c("in"))

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 5
#| fig-align: center
#| include: false

@@

ggplot(code_rel_melt_h, aes(x = code1, y = reorder(code2, total))) +
geom_tile(aes(fill = total, colour = bor_box)) + 
scale_fill_gradient2(high = "red")+
ylab("")+
xlab("")+
labs(fill = "Number of co-occurences")+
theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 14, face = "bold", color = x_colors[levels(code_rel_melt_h$code1)]), 
      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]))+
geom_text(aes(label = total))+
scale_color_manual(values = c("black", "#00000000"))+
guides(color = "none")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9
#| fig-height: 5
#| fig-align: center

@@

consv <- codes_LU %>%
  gather(col, consv_topic, reason1:reason3) %>%
  select(consv_topic)

@@

consv_bar

consv <- codes_LU %>%
  gather(col, consv_topic, reason1:reason3) %>%
  gather(test, fishery_channel, fishery_or_channel1:fishery_or_channel4) %>%
  select(c(consv_topic, fishery_channel)) %>%
  mutate(consv_bin = paste0(consv_topic, " - ", fishery_channel))

consv_s <- consv %>%
  group_by(consv_topic, consv_bin) %>%
  filter(consv_topic != "NA") %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(perc = count/sum(count)*100)

consv_bar2 <- ggplot(consv_s) +
  geom_bar(aes(x = perc, y = reorder(consv_bin, perc), fill = consv_topic), width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 45))+
  scale_y_discrete(expand = expansion(add = c(0,0))) + 
  theme(
    # Set background color to white
    panel.background = element_rect(fill = "white"),
    # Set the color and the width of the grid lines for the horizontal axis
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    # Remove tick marks by setting their length to 0
    axis.ticks.length = unit(0, "mm"),
    # Remove the title for both axes
    axis.title = element_blank(),
    # Only left line of the vertical axis is painted in black
    axis.line.y.left = element_line(color = "black"),
    # Remove labels from the vertical axis
    axis.text.y = element_blank(),
    # But customize labels for the horizontal axis
    axis.text.x = element_text(family = "Arial", size = 12)) + 
  geom_text(aes(x = perc, y = consv_bin, label = consv_bin),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    family = "Arial",
    size = 3.5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      family = "Arial",
      size = 13)
  )

consv_bar2
```

@@

#ggsave("figures/ms_figs/industry/stack_survey.png", width = 7, height = 6, units = c("in"))
#ggsave("figures/slides_svg/stack_survey.svg", width = 7, height = 6, units = c("in"))

#radar plots
freq_job_survey3 <- freq_job_survey %>%
  # group_by(fish_ship, bridge_barr) %>%
  # mutate(n_total = sum(total)) %>%
  # ungroup() %>%
  # group_by(fish_ship, bridge_barr, code_name) %>%
  # mutate(n_subtotal = sum(total)) %>%
  # reframe(value = (n_subtotal/n_total)*100) %>%
  # ungroup() %>%
  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-c(id)) %>%
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(total))

@@

top_bridge <- freq_job_survey3 %>%
  ungroup() %>%
  subset(code_name %in% top_survey$code_name) %>% 
  filter(bridge_barr == "Bridge") %>%
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

top_barrier <- freq_job_survey3 %>%
  ungroup() %>%
  subset(code_name %in% top_survey$code_name) %>%
  filter(bridge_barr == "Barrier") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

ggradar::ggradar(top_bridge,
        values.radar = c(0, 2, 4), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_br_survey.png", height = 8, width = 8, units = c("in"))
#ggsave("figures/slides_svg/radar_br.svg", height = 8, width = 8, units = c("in"))

ggradar::ggradar(top_barrier,
        values.radar = c(0, 1, 3), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
#ggsave("figures/slides_svg/radar_ba.svg", height = 8, width = 8, units = c("in"))

@@

#radar plots
freq_job_lit3 <- freq_job_lit %>%
  # group_by(fish_ship, bridge_barr) %>%
  # mutate(n_total = sum(total)) %>%
  # ungroup() %>%
  # group_by(fish_ship, bridge_barr, code_name) %>% 
  # mutate(n_subtotal = sum(total)) %>%
  # reframe(value = (n_subtotal/n_total)*100) %>%
  # ungroup() %>%
  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-c(id)) %>%
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(total))

@@

top_bridge <- freq_job_lit3 %>%
  subset(code_name %in% top_lit$code_name) %>% 
  filter(bridge_barr == "Bridge") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  ungroup() %>%
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

top_barrier <- freq_job_lit3 %>%
  subset(code_name %in% top_lit$code_name) %>%
  filter(bridge_barr == "Barrier") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  ungroup() %>%
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

ggradar::ggradar(top_bridge,
        values.radar = c(0, 15, 30), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 15, 30), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)
